Centering factor interactions

### 2016-10-25 _knitr-posts/2014-07-30-centering-interactions.Rmd
Change subheading on centering post
Fix fig

---
layout: post
title: Centering factor interactions
subtitle: Why and how you must center interactions for model averaging
published: true
---

@@

<img src="/images/interactions.png" alt="Illustration of centering interactions" width=580 height=436>

>>>>

---
layout: post
title: Centering factor interactions
subtitle: Why and how to center interactions for model averaging
published: true
---

@@

![Illustration of centering interactions](/images/interactions.png)
